%-------------------------
% Resume in Latex
% Author : Bony Roopchandani
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{0pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Bony Roopchandani} & Email : \href{mailto:bonyroopchandani@gmail.com}{bonyroopchandani@gmail.com}\\
  \href{https://bonyroopchandani.com/}{https://bonyroopchandani.com/} & Mobile : +91-8233085557 \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Hiver}{Bengaluru, India}
      {Senior Software Engineer}{May 2019 - Present}
      \resumeItemListStart
        \resumeItem{Backend}
          {Responsible for building the services on the backend as well as architecting and incorporating features.}
        \resumeItem{Frontend}
          {Developing an internal tool that helps in tracking/debugging if any/what issues can be found in a system.}
      \resumeItemListEnd
    
    
    \resumeSubheading
      {Datalicious}{Bengaluru, India}
      {Full Stack Engineer}{June 2017 - April 2019}
      \resumeItemListStart
        \resumeItem{Dashboard}
          {Responsible for implementing dashboard using React, D3, and Flask for the product which aims at providing better insights into customer journeys over a website. My responsibilities included grooming stories for a new feature, planning and managing the dashboard.}
        \resumeItem{Data Integration Service}
          {Responsible for creating an integration service which fetches data from various ad-marketing platforms and exports them to a data warehouse for further processing.}
        \resumeItem{Tag Management System}
          {Worked on the development and management of a Tag management system, that enables third-party tracking, analysis, and reporting.}
      \resumeItemListEnd

    \resumeSubheading
      {Loktra}{Bengaluru, India}
      {Full Stack Engineer}{Dec 2016 - May 2017}
      \resumeItemListStart
        \resumeItem{Field Workforce Automation Back-end}
          {Led the effort to implemented back-end from scratch using Django for automated field workforce management software.}
        \resumeItem{Location Tracking}
          {Created a horizontal scale database system to collect location coordinates from GPS devices.}
        \resumeItem{Location Analysis}
          {Implemented data pipeline to collect and clean the coordinates and create a path out of them to plot the user journeys.}
      \resumeItemListEnd
      
    \resumeSubheading
      {AppPerfect}{Udaipur, India}
      {Software Engineer}{Feb 2016 - Nov 2016}
      \resumeItemListStart
        \resumeItem{Load Test and Web Test}
          {Responsible for developing and implementing new features for Load testing and Web testing tools.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Geetanjali Institute of Technical Studies}{Udaipur, India}
      {Bachelor of Technology in Computer Science;  CGPA: 8.4/10.0}{2012 -- 2016}
  \resumeSubHeadingListEnd
  
  

% --------PROGRAMMING SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
    \resumeSubItem{Proficient}
      {: JavaScript, Python, Ruby, HTML, CSS}
    \resumeSubItem{Tools/Frameworks}
      {: React/Vue, LESS/SASS, Webpack/Gulp/Grunt, Git}
    \resumeSubItem{Data}
      {: Google BigQuery, MySQL/PostgreSQL, MongoDB}
    \resumeSubItem{Cloud Platforms}
      {: Google Cloud Platform, Amazon Web Services}
 \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://bettinza.herokuapp.com/}{Online Betting Game}}
      {Betting game made using React, HTML5.0 Canvas and Spring boot.}
    \resumeSubItem{\href{https://yazlo.herokuapp.com/}{NoOps Database Storage and Querying}}
      {Database Storage platform for managing/querying database through REST API, made using Django.}
    \resumeSubItem{\href{https://tutoschedule.herokuapp.com/}{Calendar Scheduler}}
      {Web application used by tutor for scheduling classes on his / her Google calendar by sharing scheduling link to students.}
    \resumeSubItem{\href{https://flasksocketiochat.herokuapp.com/}{Chat Application}}
      {Chatting web application developed on Flask and SocketIO, provides group and anonymous chat.}
    \resumeSubItem{\href{https://codepen.io/bony2023/}{CSS Emojis}}
      {Side hobby to create any emoji/art using just CSS.}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
